---
title: "Data Obtain"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)
library(here)
library(readr)
# devtools::install_github("abresler/nbastatR")
library(nbastatR)
library(tidyverse)
library(jsonlite)
library(sp)
library(RCurl)
# devtools::install_github("alastairrushworth/inspectdf")
library(inspectdf)
library(lubridate)
library(tidymodels)
library(cowplot)
library(reactable)
library(sparkline)

## Global options
options(max.print="75")
opts_chunk$set(echo=T,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)

col <- colorRampPalette(c("#ED7117", "#000000"))
```


# Theme for plots

```{r}
theme_bball <- function() {
  font <- "Roboto Condensed" # Assign up front
  
  theme_bw() %+replace%
  theme(
          legend.position = "none",
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5, font),
          plot.subtitle = element_text(hjust = 0.5, font),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.text.x = element_text(color = "#324D56", font),
          axis.title.y = element_text(font, angle = 90),
          axis.title.x = element_text(font),
          axis.text.y = element_text(color = "#324D56", font),
          legend.text = element_text(font),
          text = element_text(font),
          plot.background = element_rect(fill = "gray20"),
          panel.background = element_rect(fill = "gray20"),
          panel.border = element_blank())
  
}
```


# IGNORE FOR NOW
## Initial Data Obtainment

```{r eval = F}
# Read in Shot Logs Data
# Turns out NBA stopped sharing data when they partnered with Second Spectrum, looking into buying data
shot_logs <- read_csv(here("Data/shot_logs.csv"))

# Function for period to integer
game_clockinteger <- function(GAME_CLOCK) {
  sapply(strsplit(GAME_CLOCK,":"),
  function(x) {
    x <- as.numeric(x)
    x[1]+x[2]/60
    }
  )
}
# Make a time remaining variable for join
shot_logs_clean <- shot_logs %>%
  mutate(GAME_CLOCK = str_sub(GAME_CLOCK, 1, 5),
         timeRemaining = case_when(PERIOD == 1 ~ 48 - game_clockinteger(GAME_CLOCK),
                                   PERIOD == 2 ~ 36 - game_clockinteger(GAME_CLOCK),
                                   PERIOD == 3 ~ 24 - game_clockinteger(GAME_CLOCK),
                                   PERIOD == 4 ~ 12 - game_clockinteger(GAME_CLOCK)))
game_ids <- unique(shot_logs$GAME_ID) # Based on length here we have 904 unique games in the 2015-16 season
# Obtain all Play by Play Data for Specified Game IDs
pbp_df <- nbastatR::play_by_play_v2(game_ids = game_ids, nest_data = F, return_message = T)
pbp_df_clean <- pbp_df %>%
  mutate(player_name = str_to_title(player_name))
# play_by_play(game_ids = c(21700002, 21700003), nest_data = F, return_message = T) # Example for reference

# Write in data
# write_rds(here("Data/pbp_data.rds"))
# write_csv(here("Data/pbp_data.csv"))

# Join based on game, time, period, player, 
full_df <- left_join(pbp_df_clean, shot_logs, by = c("idGame" = "GAME_ID", "numberPeriod" = "PERIOD", "idPlayerNBA1" = "player_id",
                                                "namePlayer1" = "playerName", "timeRemaining"))

# Make Shot Charts

```

## Player Movement Data Obtain

```{r}
source(here("Functions/Functions.R"))
all_movements <- json_convert(here("Data/2016.NBA.Raw.SportVU.Game.Logs/0021500491.json"))
write_rds(all_movements, here("Data/all_movements1.rds"))
```

```{r}
inspectdf::show_plot(inspectdf::inspect_types(all_movements)) +
  theme_bball() +
  scale_fill_manual(values = col(2))# That's an 8 not infinity
inspectdf::show_plot(inspectdf::inspect_na(all_movements)) +# Not sure what to do about this
    theme_bball() +
  scale_fill_manual(values = col(13))
inspectdf::show_plot(inspectdf::inspect_cat(all_movements)) +
  theme_bball() +
  scale_fill_manual(values = col(104)) # Super cool that it can figure out a different palette for each bar - how is this possible?
# One dataframe is 2,343,118 observations of 13 variables
```

# Data Join

Currently just an example.

```{r echo = T}
game_id <- 0021500491
# pbp <- get_pbp(game_id) # This way sucks
pbp <- play_by_play_v2(game_ids = 0021500491) # From nbastatR

pbp <- pbp[-1,] # For some reason top observation is always NAs
# To join by
#Trying to limit the fields to join to keep the overall size manageable
pbp <- pbp %>% rename(event_id = numberEvent) %>%
  select(event_id, slugScore, descriptionPlayHome, descriptionPlayVisitor, hasVideo,
         numberEventMessageType, numberEventActionType)
# Merge
all_movements <- read_rds(here("Data/all_movements1.rds"))
# all_movements_clean <- merge(all_movements, pbp, by = "event_id", all.x = T) # Never use this again
all_movements_clean <- left_join(all_movements, pbp, by = "event_id")

write_rds(all_movements_clean, here("Data/all_movements_clean1.rds"))
```

#IGNORE FOR NOW
## Play by Play Data

Needs to have all json files at once, not sure how to run this

```{r eval = F}
# game_ids <- unique(all_movements$game_id) # Based on length here we have 904 unique games in the 2015-16 season
# Obtain all Play by Play Data for Specified Game IDs
pbp_df <- nbastatR::play_by_play_v2(game_ids = game_id, nest_data = F, return_message = T)
pbp_df_clean <- pbp_df %>%
  mutate(player_name = str_to_title(player_name))
head(pbp_df_clean)
# write_rds(here("Data/pbp_data.rds"))
# write_csv(here("Data/pbp_data.csv"))
```


It is evident that not every layup results in a made basket.

## A regression

Initial regression respectiving the shot result strata, uses number of dribbles, shot distance, and defender closeness as explanatory variables.

### Split

```{r}
shot_logs_clean <- shot_logs_clean %>% 
  mutate(SHOT_RESULT = as.factor(SHOT_RESULT))
shot_logs_split <- initial_split(shot_logs_clean, prop = 0.75, strata = "SHOT_RESULT")
shot_logs_train <- training(shot_logs_split)
shot_logs_test <- testing(shot_logs_split)

logistic_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  set_mode("classification") %>%
  fit(SHOT_RESULT ~ ., data = select(shot_logs_train, CLOSE_DEF_DIST, SHOT_DIST, DRIBBLES, SHOT_RESULT))
```

### Training models

```{r}
## get prediction on train set
pred_logit_train <- predict(logistic_fit, new_data = select(shot_logs_train, CLOSE_DEF_DIST, SHOT_DIST, DRIBBLES, SHOT_RESULT))
## get prediction on test set
pred_logit_test <- predict(logistic_fit, new_data = select(shot_logs_test, CLOSE_DEF_DIST, SHOT_DIST, DRIBBLES, SHOT_RESULT))
## get probabilities on test set
prob_logit_test <- predict(logistic_fit, new_data = select(shot_logs_test, CLOSE_DEF_DIST, SHOT_DIST, DRIBBLES, SHOT_RESULT), type="prob")
```

### Evaluating Accuracy

```{r}
# Returns accuracy and kappa
metrics(bind_cols(shot_logs_test, pred_logit_test), truth = SHOT_RESULT, estimate = .pred_class)
```

### Evaluating More Metrics

```{r}
# Returns a lot of other metrics
multimetric <- metric_set(accuracy, bal_accuracy, sens, yardstick::spec, precision, recall, ppv, npv)
multimetric(bind_cols(shot_logs_test, pred_logit_test), truth = SHOT_RESULT, estimate = .pred_class)
```

### Making an ROC Curve

```{r}
roc_auc(bind_cols(shot_logs_test, prob_logit_test), truth = SHOT_RESULT, .pred_made)
```

### Visualization of the Curve

```{r}
roc_data <- roc_curve(bind_cols(shot_logs_test, prob_logit_test), truth = SHOT_RESULT, .pred_made)
roc_data %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path() +
  geom_abline(lty = "longdash", color = "dark red") + 
  coord_equal()
```

