---
title: "Tables"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true # Other options are downcute, robobook, material, readthedown, html_clean, html_docco, lockdown, https://github.com/juba/rmdformats
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
    number_sections: true
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
library(knitr)
library(rmdformats)
library(nbastatR)
library(tidyverse)
library(here)
library(ggthemes)
library(cowplot)
library(reactable)
library(sparkline)
library(readr)
library(gganimate)
library(lubridate)

all_movements <- read_rds(here("Data/all_movements1.rds"))

all_movements_clean <- read_rds(here("Data/all_movements_clean1.rds"))

source(here("Functions/Functions.R"))
source(here("Functions/FunctionFullcourt.R"))
source(here("Functions/FunctionHalfcourt.R"))
source(here("Functions/Animation.R"))

## Global options
# options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               align = 'center')
# htmltools::tagList(rmarkdown::html_dependency_font_awesome()) # Needed so fa's in footer will show
basketball_colors <- colorRampPalette(colors = c("#bcb6ae", "#df861d", "#aa3d01", "#171820")) # Silver to light orange, orange, black
basketball_colors2 <- colorRampPalette(colors = c("#df861d", "#aa3d01", "#171820"))
basketball_palette <- c("#171820", "#fdc029", "#df861d", "#aa3d01", "#bcb6ae")
```

```{css}
.special-text {
  background-color: #FBAB00;
  border: 3px solid chocolate2;
  font-weight: bold;
}
```

```{r plot-theme}
# Theme for plots
theme_bball <- function() {
  font <- "Roboto Condensed" # Assign up front
  
  theme_bw() %+replace%
  theme(
          legend.position = "none",
          legend.title = element_blank(),
          legend.background = element_rect(fill = NA, color = NA),
          legend.key = element_rect(fill = NA, color = NA, size = 12),
          plot.title = element_text(hjust = 0.5, font, vjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, font),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.text.x = element_text(color = "#324D56", font),
          axis.title.y = element_text(font, angle = 90),
          axis.title.x = element_text(font),
          axis.text.y = element_text(color = "#324D56", font),
          legend.text = element_text(font),
          text = element_text(font),
          plot.background = element_rect(fill = "gray20"),
          panel.background = element_rect(fill = "gray20"))
  
}
```

```{r table-theme}
# Theme for tables
options(reactable.theme = reactableTheme(
  color = "hsl(233, 9%, 87%)",
  backgroundColor = "hsl(18, 56%, 0%)",
  borderColor = "hsl(233, 9%, 22%)",
  stripedColor = "hsl(233, 12%, 22%)",
  highlightColor = "hsl(233, 12%, 24%)",
  inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  style = list(fontFamily = "Roboto Condensed"),
  headerStyle = list(
    "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
  ),
  pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
))
```


# Data Testing

## Comparing player distance for misses, makes, and rebounds

Here I compare how far Dirk Nowitzki travels on misses, makes, and rebounds. Note to self that event message type is about the type of play, and event message action type is about what actually happened, consists of a ridiculous number of things that will need to be encoded, a start is recorded in Notes/Notes.txt.

```{r}
nowitzki_make <- all_movements_clean %>%
  filter(lastname == "Nowitzki" & numberEventMessageType == 1)

nowitzki_miss <- all_movements_clean %>%
  filter(lastname == "Nowitzki" & numberEventMessageType == 2)

nowitzki_rebound <- all_movements_clean %>%
  filter(lastname == "Nowitzki" & numberEventMessageType == 4)
```

```{r class.output = "special-text"}
### travel_dist takes x and y position as arguments, for example:
# Makes
travel_dist(nowitzki_make$x_loc, 
            nowitzki_make$y_loc)
# Misses
travel_dist(nowitzki_miss$x_loc, 
            nowitzki_miss$y_loc)
# Rebounds
travel_dist(nowitzki_rebound$x_loc, 
            nowitzki_rebound$y_loc)
# Let's try mapping it
makes_play_distance <- nowitzki_make %>%
  split(.$event_id) %>% #There's 44 separate dataframes here
  map_df(~ travel_dist(.$x_loc, .$y_loc)) %>%
  pivot_longer(names_to = "Play Event ID", values_to = "Distance", cols = everything()) %>%
  mutate(Type = "Makes")
# Let's try mapping it
misses_play_distance <- nowitzki_miss %>%
  split(.$event_id) %>% #There's 44 separate dataframes here
  map_df(~ travel_dist(.$x_loc, .$y_loc)) %>%
  pivot_longer(names_to = "Play Event ID", values_to = "Distance", cols = everything()) %>%
  mutate(Type = "Misses")
# Let's try mapping it
rebounds_play_distance <- nowitzki_rebound %>%
  split(.$event_id) %>% #There's 44 separate dataframes here
  map_df(~ travel_dist(.$x_loc, .$y_loc)) %>%
  pivot_longer(names_to = "Play Event ID", values_to = "Distance", cols = everything()) %>%
  mutate(Type = "Rebounds")
# Bind together
distance_df <- bind_rows(makes_play_distance, misses_play_distance, rebounds_play_distance) %>%
  mutate(`Play Event ID` = as.numeric(`Play Event ID`)) %>%
  arrange(`Play Event ID`) %>%
  mutate(row = row_number())
# Dataframe to call for legend to include means
legend_df <- distance_df %>%
  group_by(Type) %>%
  summarise(mean(Distance))
```

How should I decide which plot to do here, I think annotating substitutions on here would be great.

```{r}
# Plot, how to visualize this?
ggplot(distance_df, aes(x = `Play Event ID`, y = Distance, color = Type, group = 1)) +
  geom_line(show.legend = F) +
  geom_point() +
  # geom_smooth(span = 0.1, se = F) +
  geom_hline(aes(yintercept = mean(Distance)), linetype = "dashed", color = "orange") +
  scale_y_continuous() +
  scale_color_manual(values = c("#CF5300", "black", "#CCCCCC"), 
                     labels = paste0(legend_df$Type, ": ", round(legend_df$`mean(Distance)`, 2), " feet")) +
  labs(x = "Play of Game", title = "Dirk Nowitzki's Distance Per Play") +
  theme_bball() +
  theme(axis.text.x = element_text(color = "gray60"),
        axis.text.y = element_text(color = "gray60"),
        panel.grid = element_line(color = "gray60"),
        panel.background = element_blank(),
        legend.position = c(0.93, 0.96),
        legend.key.size = unit(0.5, "cm"))
# Or is this one better?
ggplot(distance_df, aes(x = fct_reorder(factor(`Play Event ID`), row), y = Distance, color = Type, group = 1)) +
  geom_line(show.legend = F) +
  geom_point() +
  # geom_smooth(span = 0.1, se = F) +
  geom_hline(aes(yintercept = mean(Distance)), linetype = "dashed", color = "orange") +
  scale_y_continuous() +
  scale_color_manual(values = c("#CF5300", "black", "#CCCCCC"), 
                     labels = paste0(legend_df$Type, ": ", round(legend_df$`mean(Distance)`, 2), " feet")) +
  labs(x = "Play of Game", title = "Dirk Nowitzki's Distance Per Play") +
  theme_bball() +
  theme(axis.text.x = element_text(color = "gray60"),
        axis.text.y = element_text(color = "gray60"),
        panel.grid = element_line(color = "gray60"),
        panel.background = element_blank(),
        legend.position = c(0.93, 0.96),
        legend.key.size = unit(0.5, "cm"))
```


## Comparing player distance on layups

Lets look at what players run the farthest on plays where there is a layup.

```{r}
player_layup <- all_movements_clean %>%
  filter(numberEventActionType == 5) 
dist_traveled_players <- player_layup %>% 
  mutate(lastname = paste(firstname, lastname)) %>%
  mutate(lastname = ifelse(lastname == "NA ball", "The Ball", lastname)) %>%
  group_by(lastname, event_id) %>%
 summarise(total_dist = distance_mean(x_loc, y_loc),
           velocity_mean = velocity_mean(x_loc, y_loc),
           acceleration_mean = acceleration_mean(x_loc, y_loc),
           jerk_mean = jerk_mean(x_loc, y_loc)) %>%
  group_by(lastname) %>%
  summarise(total_dist = mean(total_dist),
            velocity_mean = mean(velocity_mean),
            acceleration_mean = mean(acceleration_mean),
            jerk_mean = mean(jerk_mean)) %>%
  arrange(desc(total_dist)) %>%
  mutate(total_dist = round(total_dist, 2),
         velocity_mean = round(velocity_mean, 2),
         acceleration_mean = round(acceleration_mean, 2),
         jerk_mean = round(jerk_mean, 2))
dist_traveled_players %>%
  reactable::reactable(
    pagination = F,
    compact = T,
    borderless = F,
    striped = T,
    columns = list(
    lastname = colDef(name = "Player"),
    total_dist = colDef(name = "Total Distance",
                        style = function(value) {
                          value
                          normalized <- (value - min(dist_traveled_players$total_dist)) / 
                            (max(dist_traveled_players$total_dist) - min(dist_traveled_players$total_dist))
                          color <- basketball_colors2(normalized)
                          list(background = color)
                        },
                        class = "border-left")
  ),
  defaultColDef = colDef(footer = function(values) {
    if (!is.numeric(values)) return()
    sparkline(values, type = "box", width = 100, height = 30, 
              boxLineColor = "#FF8C00", boxFillColor = "#808080", # Silver, others are darkish orange
              whiskerColor = "#FF8C00", outlierLineColor = "#FF8C00", outlierFillColor = "#FF8C00", medianColor = "#FF8C00") # https://omnipotent.net/jquery.sparkline/#s-docs for full sparkline customization
  },
  align = "center", 
  minWidth = 100))
```

Let's compare this to the list of players that run the farthest when a layup is made.

```{r}
# Filter for layups
player_layup <- all_movements_clean %>%
  filter(numberEventActionType == 5 & numberEventMessageType == 1) 
# Get distance traveled per player on the play
dist_traveled_players <- player_layup %>% 
  mutate(lastname = paste(firstname, lastname)) %>%
  mutate(lastname = ifelse(lastname == "NA ball", "The Ball", lastname)) %>%
  group_by(lastname) %>%
 summarise(total_dist = travel_dist(x_loc, y_loc), player_id = max(player_id)) %>%
  arrange(desc(total_dist))

dist_traveled_players %>%
  reactable::reactable(columns = list(
    lastname = colDef(name = "Name"),
    total_dist = colDef(name = "Total Distance"),
    player_id = colDef(name = "Player ID")
  ),
  defaultColDef = colDef(footer = function(values) {
    if (!is.numeric(values)) return()
    sparkline(values, type = "box", width = 100, height = 30)
  }))
```


# Player Velocity, Acceleration, and Jerk

How fast does the ball move on a particular play? I choose a pass that results in a steal here.

```{r class.output = "special-text"}
event_df <- all_movements_clean %>%
  dplyr::filter(event_id == 56) %>% # Random play
  dplyr::filter(player_id == -1) %>% # Select only ball
  dplyr::filter(shot_clock != 24) # Prevent data spill over

v <- velocity(event_df$x_loc, event_df$y_loc)
v <- prepend(v, NA) # So there is the same number of columns for rejoining

event_df <- event_df %>% bind_cols(velocity = v)
ggplot(event_df, aes(x = game_clock, y = velocity)) +
  geom_point() +
  geom_line() +
  geom_smooth(span = 0.05, se = F) +
  labs(x = "Game Clock", y = "Velocity") +
  theme_bball()

paste("The mean velocity of the ball on this play is", 
      mean(v, na.rm = T), "units/unit.") # Mean velocity of the ball is 872, not sure how to convert that
```

## Acceleration

```{r}
# Change ball name, give players one name
acceleration_df <- all_movements_clean %>%
  mutate(name = paste(firstname, lastname)) %>%
  mutate(name = ifelse(name == "NA ball", "The Ball", name)) %>%
  group_by(event_id, name) %>%
  summarise(acceleration = mean(acceleration(x_loc, y_loc))) %>%
  arrange(event_id)
# Plot each player's acceleration over the course of the game
ggplot(acceleration_df, aes(x = event_id, y = acceleration, color = name)) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = basketball_colors(25)) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6), labels = scales::comma) +
  labs(x = "Play of Game", y = "Acceleration (idk units yet)", title = "Acceleration Per Player") +
  facet_wrap(~ name) +
  theme_bball()
```


## Jerk

How should I do substitutions?

```{r}
# Change ball name, give players one name
jerk_df <- all_movements_clean %>%
  mutate(name = paste(firstname, lastname)) %>%
  mutate(name = ifelse(name == "NA ball", "The Ball", name)) %>%
  group_by(event_id, name) %>%
  summarise(jerk = mean(jerk(x_loc, y_loc))) %>%
  arrange(event_id)
# Plot each player's jerk over the course of the game, which will obviously be the same graph
ggplot(jerk_df, aes(x = event_id, y = jerk, color = name)) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = basketball_colors(25)) +
  facet_wrap(~ name) +
  theme_bball() 
```

# Convex Hulls and Image Making

An NBA court is 94 feet by 50 feet. In the data x_loc (the x location variable) has a minimum, and maximum of (-5.22728, 98.53855), y_loc (the y location variable) is (-3.27955, 52.23675). It is safe to assume that the negative distances are just out of bounds, and mostly - presumably - the ball or inbounds passes.

## Player positions

Let's see where player's are when the ball crosses the 28' line (the three point line) on a given play. Here I choose Gerald Green making a 14' pull-up jump shot.

```{r}
# Select event
event_394 <- all_movements_clean %>% 
  filter(event_id == 394) %>%
  arrange(desc(game_clock))
# Select max time
balltime <- event_394 %>%
  filter(player_id == -1) %>%
  summarise(clock28 = max(game_clock[x_loc < 28])) %>%
  deframe()
# What does this look like grouped
all_movements_clean %>%
  group_by(event_id) %>%
  filter(player_id == -1) %>%
  summarise(clock28 = max(game_clock[x_loc < 28], na.rm = T),
            descriptionPlayHome = unique(descriptionPlayHome))
# Find player positions at time [balltime], gives a dataframe of 10 players which makes sense
player_pos <- event_394 %>%
  filter(game_clock == balltime) %>%
  filter(player_id != -1) %>% # Don't record the ball
  mutate(name = paste(firstname, lastname)) %>%
  select(x_loc, y_loc, name, team_id) %>%
  rename_all( ~ str_to_title(.))
player_pos %>%
  reactable()
```

## Calculating the "Convex Hull"

We have to do this separately, for the defensive and offensive teams, although there could be interesting results for convex hulls by types of players.

```{r}
# Select defense x and y
player_pos_defense <- player_pos %>%
  filter(Team_id == min(Team_id)) %>%# This chooses the mavericks, the defensive team
  select(X_loc, Y_loc) # They all appear very close to each other, looks good
# Calculate convex hull
chull1 <- chull(player_pos_defense) 
chull2 <- c(chull1, chull1[1]) # 5 points needed for four line segments, add first set of points at the end
df_pos <- as_tibble(bind_cols(ID = 1, 
                              X = player_pos_defense[chull2,]$X_loc, 
                              Y = player_pos_defense[chull2,]$Y_loc))
area_def <- round(chull_area(df_pos$X, df_pos$Y), 2)
# Plot the hull with names
df_pos %>% 
  left_join(player_pos, by = c("X" = "X_loc", "Y" = "Y_loc")) %>%
  ggplot(aes(x = X, y = Y)) +
  geom_polygon(color = "white", fill = "orange") +
  geom_text(aes(label = paste("Convex Hull Area =", area_def), x = mean(df_pos$X), y = mean(df_pos$Y))) +
  geom_text(aes(label = Name)) +
  theme_bball() # Would be cool to rotate names based on polygon segments?
```

## Plotting on a Court

It looks like this play starts on an inbound.

```{r}
# I just have to make this sort by event id, and for a full court for a really useful function
# Right now let's just animate this play, which should go by row number
dplayer <- player_position(eventID = 394, gameClock = balltime, df = all_movements_clean) # Going to have to do something about time call here
dchull <- chull_plot(eventID = 394, gameClock = balltime, df = all_movements_clean) # Tibbles get wack here
dcentroid <- chull_plot_centroid(eventID = 394, gameClock = balltime, df = all_movements_clean) # Bind_rows requires names, use rbind in the function instead

plot_court(court_themes_half$light) +
  # Add players
  geom_point(data = dplayer, aes(x = X, y = Y, group = ID), 
             color = dense_rank(dplayer$`ID`), size = 5) +
  geom_text(data = dplayer, aes(label = NAME, x = X, y = Y, group = ID), vjust = -1) +
  scale_colour_brewer() +
  # Add Convex hull areas
  geom_polygon(data = dchull, aes(x = X, y = Y, group = ID),
               fill = dense_rank(dchull$ID), alpha = 0.2) +
  scale_fill_brewer() +
  # Add Centroids
  scale_shape_identity() +
  geom_point(data = dcentroid, aes(x = X, y = Y, group = ID),
             color = (dcentroid$ID), size = 3, shape = 13) +
  geom_text(data = dcentroid, aes(x = X, y = Y, group = ID),
             color = (dcentroid$ID), size = 3, label = "Centroid:", hjust = 1.2)
```

## Quick Interlude of Team Color Data

```{r}
team_names <- read_rds(here("Data/team_id.rds"))
team_colors <- teamcolors %>% filter(league == "nba")
color_names <- team_names %>%
  mutate(idTeam = factor(idTeam)) %>%
  left_join(select(team_colors, primary, logo, name), by = c("nameTeam" = "name"))
```

## Animating Play 394

```{r}
# Dataframe for play 394, groups by shot clock to make group id and identifies ball and player
anim_394 <- event_394 %>%
  mutate(group_id = dense_rank(desc(game_clock))) %>%
  relocate(group_id, .before = event_id) %>%
  mutate(value = case_when(player_id == -1 ~ "ball",
                           player_id != -1 ~ "player"),
         team_id = factor(team_id),
         quarter_annotate = case_when(quarter == 4 ~ "4th",
                                      quarter == 3 ~ "3rd",
                                      quarter == 2 ~ "2nd",
                                      quarter == 1 ~ "1st",
                                      quarter == 5 ~ "5th",
                                      quarter == 6 ~ "6th",
                                      quarter == 7 ~ "7th",
                                      quarter == 8 ~ "8th"),
         clock_annotate = game_clock_reformat(game_clock)) %>%
    left_join(select(color_names, primary, nameTeam, logo, idTeam), by = c("team_id" = "idTeam")) # Need to make sure this encodes by defense or offense later, add team colors as well

# Calculating the chull
chull_394 <- anim_394 %>%
  filter(value != "ball") %>%
  group_by(group_id, team_id) %>%
  nest() %>%
  mutate(
    hull = map(data, ~ with(.x, chull_plot2(x_loc, y_loc))),
    out = map2(data, hull, ~ .x[.y, , drop = F])
  ) %>%
  select(-data) %>%
  unnest(cols = c(hull, out)) %>%
  group_by(group_id, team_id) %>%
  mutate(centroid_x = mean(x_loc),
            centroid_y = mean(y_loc)) %>%
  ungroup() #%>% # Did I do this correctly?
  # rename(chull_id = group_id)
  

# Plot then add gganimate?
# p <- fullcourt() +
#   # Add Players
#   geom_point(data = filter(anim_394, value == "player"), 
#              aes(x = x_loc, y = y_loc, group = team_id, color = team_id), size = 5) +
#   geom_text(data = filter(anim_394, value == "player"), 
#             aes(x = x_loc, y = y_loc, group = team_id, label = paste(firstname, lastname)), 
#             vjust = -1, color = "black") +
#   scale_color_manual(values = c("steelblue", "orangered"), labels = c("Dallas Mavericks", "Miami Heat")) +
#   geom_point(data = filter(anim_394, value == "ball"), color = "darkorange", size = 3, aes(x = x_loc, y = y_loc)) + # Add ball
#   # Add Convex hull areas
#   geom_polygon(data = chull_394, aes(x = x_loc, y = y_loc, group = team_id, fill = team_id),
#                alpha = 0.2) +
#   scale_fill_manual(values = c("steelblue", "orangered")) +
#   # Add Centroids
#   geom_point(data = chull_394, aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
#              size = 3, shape = 13) +
#   geom_text(data = chull_394, aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
#              size = 3, label = "Centroid:", hjust = 1.2) +
#   labs(title = "{current_frame}") # Needs fixing this literally doesn't ever load???
# 
# # Animated version
# anim_final <- p + transition_manual(frames = game_clock)
# animated <- animate(anim_final, 
#                     width = 800,
#                     height = 800,
#                     nframes = length(unique(anim_394$game_clock)),
#                     fps = 10,
#                     res = 150,
#                     end_pause = 0)
# anim_save(here("Gifs/394_0021500491.gif"), animated)

# With transition_state
p2 <- fullcourt(court_themes$light) +
  # Add Players
  geom_point(data = filter(anim_394, value == "player"), 
             aes(x = x_loc, y = y_loc, group = team_id, color = team_id), size = 5) +
  geom_text(data = filter(anim_394, value == "player"), 
            aes(x = x_loc, y = y_loc, group = team_id, label = paste(firstname, lastname)), 
            vjust = -1, color = "black", family = "Roboto Condensed") +
  scale_color_manual(values = c(dplyr::filter(anim_394, team_value == "home") %>% select(primary) %>% unique() %>% deframe(),
                       dplyr::filter(anim_394, team_value == "away") %>% select(primary) %>% unique() %>% deframe()), 
                     labels = c(dplyr::filter(anim_394, team_value == "home") %>% select(nameTeam) %>% unique() %>% deframe(),
                                dplyr::filter(anim_394, team_value == "away") %>% select(nameTeam) %>% unique() %>% deframe())) +
  geom_point(data = filter(anim_394, value == "ball"), color = "darkorange", size = 3, aes(x = x_loc, y = y_loc)) + # Add ball
  # Add Convex hull areas
  geom_polygon(data = chull_394, aes(x = x_loc, y = y_loc, group = team_id, fill = team_id),
               alpha = 0.2, show.legend = F) +
  scale_fill_manual(values = c(dplyr::filter(anim_394, team_value == "home") %>% select(primary) %>% unique() %>% deframe(),
                      dplyr::filter(anim_394, team_value == "away") %>% select(primary) %>% unique() %>% deframe())) +
  # Add Centroids
  geom_point(data = chull_394, aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
             size = 3, shape = 13) +
  geom_text(data = chull_394, aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
             size = 3, label = "Centroid:", hjust = 1.2, show.legend = F, family = "Roboto Condensed") +
  # Add shot clock
  geom_text(data = anim_394, aes(x = 62.5+2, y = 57.5, label = shot_clock), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") + # Why is geom_text always so ugly
  # Add game clock
  geom_text(data = anim_394, aes(x = 56.25+2, y = 57.5, label = clock_annotate), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") +
  # Add quarter
  geom_text(data = anim_394, aes(x = 48.75+2, y = 57.5, label = str_to_upper(quarter_annotate)), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") +
  ggtitle(paste("Current Score:", anim_394$slugScore))
anim_test <- p2 + transition_states(states = group_id)
animated_test <- animate(anim_test, 
                    width = 1725.450,
                    height = 913.636,
                    nframes = (length(unique(anim_394$group_id))/2),
                    fps = 20,
                    res = 100,
                    end_pause = 0) # ISSUES: SCORE DOES NOT CHANGE, IN THIS PART OF DATA, EVENT ID IS SUBSET WEIRDLY AND INCLUDES A LOT AFTER THE PLAY
animated_test
# anim_save(here("Gifs/394_0021500491_04.gif"), animated_test)
```


## FOR TESTING

```{r include = F}
# Can I join these? Seems impossible since chull has to be longer
# test_join <- anim_394 %>% left_join(select(chull_394, x_loc, y_loc, centroid_x, centroid_y, group_id), by = c("group_id"))
# img <- (dplyr::filter(anim_394, team_value == "home") %>% select(logo) %>% unique() %>% pull(logo))
# img_read <- caTools::read.gif(img, frame = 1)
# mat <- img$col[img$image+1]
# For adding logo, doesn't work currently

test_gif <- fullcourt(court_themes$light) +
  # Add Players
  geom_point(data = filter(anim_394[1:22,], value == "player"), 
             aes(x = x_loc, y = y_loc, group = team_id, color = team_id), size = 5) +
  geom_text(data = filter(anim_394[1:22,], value == "player"), 
            aes(x = x_loc, y = y_loc, group = team_id, label = paste(firstname, lastname)), 
            vjust = -1, color = "black", family = "Roboto Condensed") +
  scale_color_manual(values = c(dplyr::filter(anim_394, team_value == "home") %>% select(primary) %>% unique() %>% deframe(),
                       dplyr::filter(anim_394, team_value == "away") %>% select(primary) %>% unique() %>% deframe()), 
                     labels = c(dplyr::filter(anim_394, team_value == "home") %>% select(nameTeam) %>% unique() %>% deframe(),
                                dplyr::filter(anim_394, team_value == "away") %>% select(nameTeam) %>% unique() %>% deframe())) +
  geom_point(data = filter(anim_394[1:22,], value == "ball"), color = "darkorange", size = 3, aes(x = x_loc, y = y_loc)) + # Add ball
  # Add Convex hull areas
  geom_polygon(data = chull_394[1:24,], aes(x = x_loc, y = y_loc, group = team_id, fill = team_id),
               alpha = 0.2, show.legend = F) +
  scale_fill_manual(values = c(dplyr::filter(anim_394, team_value == "home") %>% select(primary) %>% unique() %>% deframe(),
                      dplyr::filter(anim_394, team_value == "away") %>% select(primary) %>% unique() %>% deframe())) +
  # Add Centroids
  geom_point(data = chull_394[1:24,], aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
             size = 3, shape = 13) +
  geom_text(data = chull_394[1:24,], aes(x = centroid_x, y = centroid_y, group = team_id, color = team_id),
             size = 3, label = "Centroid:", hjust = 1.2, show.legend = F, family = "Roboto Condensed") +
  # Add shot clock
  geom_text(data = anim_394[1:22,], aes(x = 62.5+2, y = 57.5, label = shot_clock), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") + # Why is geom_text always so ugly
  # Add game clock
  geom_text(data = anim_394[1:22,], aes(x = 56.25+2, y = 57.5, label = clock_annotate), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") +
  # Add quarter
  geom_text(data = anim_394[1:22,], aes(x = 48.75+2, y = 57.5, label = str_to_upper(quarter_annotate)), 
            size = 6, color = "#BF0A30", family = "Roboto Condensed", fontface = "bold") +
  ggtitle(paste("Current Score:", anim_394$slugScore))
anim__gif_test <- test_gif + transition_manual(frames = group_id)
final_test <- animate(anim__gif_test, 
                    width = 1725.450,
                    height = 913.636,
                    nframes = 2,
                    fps = 20,
                    res = 100,
                    end_pause = 0) # ISSUES: SCORE DOES NOT CHANGE, IN THIS PART OF DATA, EVENT ID IS SUBSET WEIRDLY AND INCLUDES A LOT AFTER THE PLAY
# anim_save(here("Gifs/test.gif"), final_test)
```

# Testing Out Functions

```{r}
# All Dunks in this game
all_movements_clean %>% 
  filter(str_detect(descriptionPlayHome, "Dunk|dunk") == T | str_detect(descriptionPlayVisitor, "Dunk|dunk") == T) %>% 
  select(event_id) %>% 
  unique()

anim_149 <- animate_play(all_movements_clean, 149)
anim_149
# anim_save(here("Gifs/149_0021500491_01.gif"))

anim_149_quick <- animate_play_quick(all_movements_clean, 149)
anim_149_quick
# anim_save(here("Gifs/149_0021500491_quick_01.gif"))
```

